---
title: "R Notebook"
output: html_document
---


```{r}

library(tidyverse, quiet=TRUE) # data wrangling and visualization
library(lme4, quiet=TRUE)     # "golden standard" for mixed-effects modelling in R (no p-values)
library(lmerTest, quiet=TRUE)  # p-values for MEMs based on the Satterthwaite approximation
library(psycho, quiet=TRUE)   # mainly for an "analyze()" function
library(broom, quiet=TRUE)     # for tidy results
library(knitr, quiet=TRUE)     # beautifying tables
library(sjPlot, quiet=TRUE)    # for visualising MEMs
library(effects, quiet=TRUE)   # for visualising MEMs
library(report, quiet=TRUE)    # for describing models
library(emmeans, quiet=TRUE)   # for post-hoc analysis
library(equatiomatic, quiet=TRUE) # for extracting the equation
library(gridExtra) # for grid.arrange() to print plots side-by-side
library(ufs, quiet=TRUE) # For multiple choices questions analysis
```

```{r}
# Set up the script folder as working directory
library(rstudioapi)

# Getting the path of your current open file
current_path = rstudioapi::getActiveDocumentContext()$path 
setwd(dirname(current_path ))
print( getwd() )
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="./plots/")
```

# Load the full dataset
```{r}
df_all = read_csv('/home/olivier/git/pro/bsc/experiment-platform/data/cleaned_dataset_per_news.csv')

```

# Function to test overdispersion
source: http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#overdispersion

```{r}

overdisp_fun <- function(model) {
  rdf <- df.residual(model)
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }

```


### Subsetting the df

```{r}

fixed_effects <- c('Political', 'type_news', 'Education2', 'Education',
                   'Technological', 'Religion', 'Gender', 'Age')
random_effects <- c('id_sondea', 'news_title')
dep_var <- c('answer')
all_var <- c(fixed_effects, random_effects, dep_var)

df_education <- df_all[,all_var] 

df_education[sapply(df_education, is.character)] <- lapply(df_education[sapply(df_education, is.character)], 
                                                           as.factor)

# If want to predict the Right, need to ref "Wrong". No idea why, it is just how it works!
df_education$answer = relevel(df_education$answer, ref="Wrong")
df_education$type_news = relevel(df_education$type_news, ref="true_news")


df_education$Education= relevel(df_education$Education, ref="No university studies")
df_education$Education2= factor(df_education$Education2, levels= c("Secondary", 'College', "University"))

df_education$Technological = factor(df_education$Technological
                                    , levels= c("Basic", "Intermediate", "Advanced"))

df_education$Political = relevel(df_education$Political, ref="Right")
df_education$Religion = relevel(df_education$Religion, ref="Religious")
df_education$Age = factor(df_education$Age, levels=c("<=18-34", "35-54", ">55" ))
df_education$Gender = relevel(df_education$Gender, ref='Male')


df_education <- df_education %>% drop_na()

df_education$answer.num = as.numeric(df_education$answer)-1
```



## Plotting the EDA on the random effects
```{r}

day19Plot1 <- ggplot(aes(x=type_news, y=answer.num), data=df_education) + 
  stat_summary(fun.data="mean_cl_boot", geom='line', aes(group=news_title)) +
  coord_cartesian(ylim=c(0,0.6)) + 
  ylab("% Answer by Title") 

day19Plot2 <- ggplot(aes(x=type_news, y=answer.num), data=df_education) + 
  stat_summary(fun.data="mean_cl_boot", geom='line', aes(group=id_sondea)) + 
  coord_cartesian(ylim=c(0,0.6)) + 
  ylab("% Answer by Subject") 

grid.arrange(day19Plot1, day19Plot2, ncol = 2)
```

# Analysis

## Model without interactions

```{r}
m1_equation = paste0("answer ~ ",
                     "Political",
                     "+ Education2",
                     "+ Gender",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news",
                     "+ (1 | news_title)",
                     "+ (type_news| news_title)",
                     "+ (1 | id_sondea)"
                     )

m1 <- glmer(m1_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
summary(m1, corr=FALSE)
```

```{r m1_effects, fig.width = 8, fig.height = 7}
plot(allEffects(m1))
```

```{r m1_odd_ratios, fig.width = 5, fig.height = 5}
plot_model(m1, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```


## Model with interaction terms on the type_news, technology and education
```{r}
m2_equation = paste0("answer ~ ",
                     "+ Education2",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news",
                     "+ Political",
                     "+ Gender",
                     
                     "+ Education2*Age",
                     "+ Education2*Religion", 
                     "+ Education2*Technological",
                     "+ Education2*type_news",
                     "+ Education2*Political",
                     "+ Education2*Gender",
                     
                     
                     "+ Age*Religion",
                     "+ Age*Technological",
                     "+ Age*type_news",
                     "+ Age*Political",
                     "+ Age*Gender",


                     "+ Technological*type_news",
                     "+ Technological*Political",
                     "+ Technological*Gender",
                     
                     "+ Political*type_news",
                     "+ Political*Gender",
                     
                     "+Gender*type_news",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")


# Model with all interactions
m2 <- glmer(m2_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))

```

```{r}
summary(m2, corr=FALSE)
```

```{r m2_effects, fig.width = 18, fig.height =15}
plot(allEffects(m2), multiline=TRUE,confint=TRUE,ci.style="bars")
```

```{r m2_odd_ratios, fig.width = 15, fig.height = 20}

plot_model(m2, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```

```{r}
tab_model(m2)
```

## Model with selected interactions and main effects
```{r}
m3_equation = paste0("answer ~ ",
                     "+ Education2",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news",
                     "+ Political",

                     "+ Age*Education2",
                     "+ Education2*type_news",
                     #"+ Education2*Political",

                     
                     "+ Age*type_news",
                     "+ Age*Political",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")




m3 <- glmer(m3_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}

capture.output(summary(m3, corr=FALSE),file="./tables/parc_sum.txt")
summary(m3, corr=FALSE)

```

```{r m3_effects, fig.width = 15, fig.height = 8}
plot(allEffects(m3), multiline=TRUE,confint=TRUE)#,ci.style="bars")
```

```{r m3_odd_ratios, fig.width = 8, fig.height = 7}
plot_model(m3, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```


```{r}
tab_model(m3)
```


## Selection of the model

```{r}
anov <- anova(m2,m3, m1)
capture.output(summary(anov),file="./tables/anova_model_selection.txt")
anov
```

## Doing simple Logistic regression without any random effects
```{r}
log_equation  = paste0("answer ~ ",
                       "Political",
                                    "+ Education",
                                    "+ Gender",
                                    "+ Age",
                                    "+ Religion",
                                    "+ Technological",
                                    "+ type_news",
                                    "+ Education*type_news",
                                    "+ Gender*type_news",
                                    "+ Age*type_news",
                                    "+ Religion*type_news",
                                    "+ Technological*type_news",
                                    "+ Political*type_news"
                       )
            
log1= glm(log_equation,
          data=df_education, 
          family="binomial")

```

```{r}
summary(log1, corr=FALSE)
```

```{r log1_effects}
plot(allEffects(log1))
```

```{r log1_odd_ratios}

plot_model(log1, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```

```{r}
tab_model(log1)
```



# Analysis for justifications


```{r}
var_just_fake <- c("Previously_read_debunked",
                 "Source_unknown",
                 "Media_unreliable",
                 "Cited_sources_unknown",
                 "Cited_sources_unreliable",
                 "Without_sources",
                 "Unprofessional_style",
                 "No_coherent",
                 "Headline_sensationalist",
                 "Image_sensationalist",
                 "Different_belief",
                 "Different_ideology",
                 "Other")

var_just_true <- c("Previously_read_the_information",
                 "Known_media",
                 "Reliable_media",
                 "Source_known",
                 "Source_Reliable",
                 "Professional_style",
                 "Coherent",
                 "Same_belief",
                 "Same_ideology",
                 "Other")


```

## Justification, people getting wrong on Misinformation

```{r}  
df_fake_wrong <- df_all[str_detect(df_all$type_news, 'fake_news') | str_detect(df_all$answer, 'Wrong')  , ]

all_var <- c(var_just_true)

df_fake_wrong <- df_fake_wrong[,all_var] 

multiFreq_fake_wrong <- multiResponse(df_fake_wrong, var_just_true)
write.csv(multiFreq_fake_wrong, "./tables/justification_fake_wrong.csv", row.names = FALSE)

multiFreq_fake_wrong
```
## Justification, people getting Right on Legitimate information

```{r}  
df_true_right <- df_all[str_detect(df_all$type_news, 'true_news') | str_detect(df_all$answer, 'Right')  , ]

all_var <- c(var_just_true)

df_true_right <- df_true_right[,all_var] 

multiFreq_true_right <- as.data.frame(multiResponse(df_true_right, var_just_true))
write.csv(multiFreq_true_right, "./tables/justification_true_right.csv", row.names = FALSE)

multiFreq_true_right
```



## Justification, people getting Right on Misinformation information


```{r}
df_fake_right <- df_all[str_detect(df_all$type_news, 'fake_news') | str_detect(df_all$answer, 'Right')  , ]

all_var <- c(var_just_fake)

df_fake_right <- df_fake_right[,all_var] 

multiFreq_fake_right <- as.data.frame(multiResponse(df_fake_right, var_just_fake))
write.csv(multiFreq_fake_right, "./tables/justification_fake_right.csv", row.names = FALSE)

multiFreq_fake_right

```

## Justification, people getting Wrong on Legitimate information

```{r}
df_true_wrong <- df_all[str_detect(df_all$type_news, 'true_news') | str_detect(df_all$answer, 'Wrong')  , ]

all_var <- c(var_just_fake)

df_true_wrong <- df_true_wrong[,all_var] 

multiFreq_true_wrong <- as.data.frame(multiResponse(df_true_wrong, var_just_fake))
write.csv(multiFreq_true_wrong, "./tables/justification_true_wrong.csv", row.names = FALSE)

multiFreq_true_wrong

```


## Analysis for actions

```{r}

action_var <- c('share_friends_and_family', 'share_online', 'verify_source', "apply_learning", 'no_action')
fixed_effects <- c('Political', 'type_news', 'Education2', 'Education',
                   'Technological', 'Religion', 'Gender', 'Age', 'answer')
random_effects <- c('id_sondea', 'news_title')
all_var <- c(action_var, fixed_effects,  random_effects)

df_actions <- df_all[,all_var] 

df_actions[sapply(df_actions, is.character)] <- lapply(df_actions[sapply(df_actions, is.character)], 
                                                           as.factor)
# If want to predict the Right, need to ref "Wrong". No idea why, it is just how it works!
df_actions$answer = relevel(df_actions$answer, ref="Wrong")
df_actions$type_news = relevel(df_actions$type_news, ref="true_news")




df_actions$answer = relevel(df_actions$answer, ref="Wrong")
df_actions$type_news = relevel(df_actions$type_news, ref="true_news")


df_actions$Education= relevel(df_actions$Education, ref="No university studies")
df_actions$Education2= factor(df_actions$Education2, levels= c("Secondary", 'College', "University"))

df_actions$Technological = factor(df_actions$Technological
                                    , levels= c("Basic", "Intermediate", "Advanced"))

df_actions$Political = relevel(df_actions$Political, ref="Right")
df_actions$Religion = relevel(df_actions$Religion, ref="Religious")
df_actions$Age = factor(df_actions$Age, levels=c("<=18-34", "35-54", ">55" ))
df_actions$Gender = relevel(df_actions$Gender, ref='Male')

df_actions <- df_actions[!is.na(df_actions$answer),]
```


```{r}
#for (i in action_var) {
 
  #model_equation <- paste0(i, ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
  
 # print(model_equation)
  
#  model <- glmer(model_equation,
     #         data=df_actions, 
    #          family="binomial", 
   #           control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
  #print(summary(model, corr=FALSE))
  
 # plot_effect_name <- paste0('./plots/action_', i, '_effects.jpg')
 # jpeg(file=plot_effect_name, width = 350, height = 350)
  
  #plot(allEffects(model))
  #dev.off()
  
 # plot_odds_name <- paste0('./plots/action_', i, '_odds.jpg')
#  jpeg(file=plot_odds_name, width = 350, height = 350)
  
  #plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)
  #dev.off()}
```


### share_friends_and_family
```{r}

df_mod <- df_actions[!is.na(df_actions$share_friends_and_family),]

model_equation <- paste0('share_friends_and_family', ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
model <- glmer(model_equation,
              data=df_mod, 
              family="binomial", 
              control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
print(summary(model, corr=FALSE))
```

```{r actions_share_friends_and_family_effects, fig.width = 7, fig.height = 5}
plot(allEffects(model))
```

```{r actions_share_friends_and_family_odd_ratios, fig.width = 4, fig.height = 4}
plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)

```

### share_online
```{r}

df_mod <- df_actions[!is.na(df_actions$share_online),]

model_equation <- paste0('share_online', ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
model <- glmer(model_equation,
              data=df_mod, 
              family="binomial", 
              control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
print(summary(model, corr=FALSE))
```

```{r actions_share_online_effects, fig.width = 7, fig.height = 5}
plot(allEffects(model))
```

```{r actions_share_online_odd_ratios, fig.width = 4, fig.height = 4}

plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)

```

### verify_source

```{r}
df_mod <- df_actions[!is.na(df_actions$verify_source),]

model_equation <- paste0('verify_source', ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
model <- glmer(model_equation,
              data=df_mod, 
              family="binomial", 
              control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
print(summary(model, corr=FALSE))
```

```{r actions_verify_source_effects, fig.width = 7, fig.height = 5}
plot(allEffects(model))
```

```{r actions_verify_source_odd_ratios, fig.width = 4, fig.height = 4}

plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)

```

### apply_learning
```{r}
df_mod <- df_actions[!is.na(df_actions$apply_learning),]

model_equation <- paste0('apply_learning', ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
model <- glmer(model_equation,
              data=df_mod, 
              family="binomial", 
              control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
print(summary(model, corr=FALSE))
```

```{r actions_apply_learning_effects, fig.width = 7, fig.height = 5}
plot(allEffects(model))
```

```{r actions_apply_learning_odd_ratios, fig.width = 4, fig.height = 4}
plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)

```

### no_action

```{r}
df_mod <- df_actions[!is.na(df_actions$no_action),]

model_equation <- paste0('no_action', ' ~ answer + Age + Technological +(1 | news_title) + (1 | id_sondea)')
model <- glmer(model_equation,
              data=df_mod, 
              family="binomial", 
              control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
print(summary(model, corr=FALSE))
```

```{r actions_no_action_effects, fig.width = 7, fig.height = 5}
plot(allEffects(model))
```

```{r actions_no_action_odd_ratios, fig.width = 4, fig.height = 4}

plot_model(model, vline.color = "red", sort.est = TRUE, show.values = TRUE, value.offset = .3)

```


