---
title: "R Notebook"
output: html_document
---

```{r}

library(tidyverse, quiet=TRUE) # data wrangling and visualization
library(lme4, quiet=TRUE)     # "golden standard" for mixed-effects modelling in R (no p-values)
library(lmerTest, quiet=TRUE)  # p-values for MEMs based on the Satterthwaite approximation
library(psycho, quiet=TRUE)   # mainly for an "analyze()" function
library(broom, quiet=TRUE)     # for tidy results
library(knitr, quiet=TRUE)     # beautifying tables
library(sjPlot, quiet=TRUE)    # for visualising MEMs
library(effects, quiet=TRUE)   # for visualising MEMs
library(report, quiet=TRUE)    # for describing models
library(emmeans, quiet=TRUE)   # for post-hoc analysis
library(equatiomatic, quiet=TRUE) # for extracting the equation
library(gridExtra) # for grid.arrange() to print plots side-by-side
library(ufs, quiet=TRUE) # For multiple choices questions analysis
library(afex, quiet=TRUE) # For automatic likelihood Ratio Test
```

```{r}
# Knowing package and R version
packageVersion('lme4')
citation('lme4')
```

```{r}
# Set up the script folder as working directory
library(rstudioapi)

# Getting the path of your current open file
current_path = rstudioapi::getActiveDocumentContext()$path 
setwd(dirname(current_path ))
print( getwd() )
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="./plots/")
```

# Load the full dataset
```{r}
df_all = read_csv('../data/cleaned_dataset_per_news.csv')
```

# Function to test overdispersion (not needed for logistic function)
source: http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#overdispersion

```{r}

overdisp_fun <- function(model) {
  rdf <- df.residual(model)
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }

```


### Subsetting the df

```{r}

fixed_effects <- c('Political', 'type_news', 'Education2', 'Education',
                   'Technological', 'Religion', 'Gender', 'Age')
random_effects <- c('id_sondea', 'news_title')
dep_var <- c('answer')
all_var <- c(fixed_effects, random_effects, dep_var)

df_education <- df_all[,all_var] 

df_education[sapply(df_education, is.character)] <- lapply(df_education[sapply(df_education, is.character)], 
                                                           as.factor)

# If want to predict the Right, need to ref "Wrong". No idea why, it is just how it works!
df_education$answer = relevel(df_education$answer, ref="Wrong")
df_education$type_news = relevel(df_education$type_news, ref="true_news")


df_education$Education= relevel(df_education$Education, ref="No university studies")
df_education$Education2= factor(df_education$Education2, levels= c("Secondary", 'College', "University"))

df_education$Technological = factor(df_education$Technological
                                    , levels= c("Basic", "Intermediate", "Advanced"))

df_education$Political = relevel(df_education$Political, ref="Right")
df_education$Religion = relevel(df_education$Religion, ref="Religious")
df_education$Age = factor(df_education$Age, levels=c("<=18-34", "35-54", ">55" ))
df_education$Gender = relevel(df_education$Gender, ref='Male')


df_education <- df_education %>% drop_na()

df_education$answer.num = as.numeric(df_education$answer)-1
```



## Plotting the EDA on the random effects
```{r}

day19Plot1 <- ggplot(aes(x=type_news, y=answer.num), data=df_education) + 
  stat_summary(fun.data="mean_cl_boot", geom='line', aes(group=news_title)) +
  coord_cartesian(ylim=c(0,0.6)) + 
  ylab("% Answer by Title") 

day19Plot2 <- ggplot(aes(x=type_news, y=answer.num), data=df_education) + 
  stat_summary(fun.data="mean_cl_boot", geom='line', aes(group=id_sondea)) + 
  coord_cartesian(ylim=c(0,0.6)) + 
  ylab("% Answer by Subject") 

grid.arrange(day19Plot1, day19Plot2, ncol = 2)
```

# Analysis


```{r}

m0_equation = paste0("answer ~ ",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m0 <- glmer(m0_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}

m1_equation = paste0("answer ~ ",
                     "+ type_news",

                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m1 <- glmer(m1_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m2_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",

                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m2 <- glmer(m2_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m3_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m3 <- glmer(m3_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m4_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",

                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m4 <- glmer(m4_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}

m5_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",

                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m5 <- glmer(m5_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m6_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m6 <- glmer(m6_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}

m7_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m7 <- glmer(m7_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```
```{r}

m8_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ type_news*Education2",
                     "+ type_news*Age",
                     "+ type_news*Religion",
                     "+ type_news*Technological",
                     "+ type_news*Political",
                     "+ type_news*Gender",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m8 <- glmer(m8_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

## Selection of the model

```{r}
anov <- anova(m1,m2, m3, m4, m5, m6, m7, m8)
capture.output(summary(anov),file="./tables/anova_model_selection.txt")
anov
```

```{r}

m9_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ Education2*Age",
                     "+ Education2*Religion", 
                     "+ Education2*Technological",
                     "+ Education2*Political",
                     "+ Education2*Gender",
                     "+ Education2*type_news",

                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m9 <- glmer(m9_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m10_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ Age*Religion",
                     "+ Age*Technological",
                     "+ Age*Political",
                     "+ Age*Gender",
                     "+ Age*type_news",
                     "+ Age*Education2",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m10 <- glmer(m10_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m11_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ Religion*Technological",
                     "+ Religion*Political",
                     "+ Religion*Gender",
                     "+ Religion*type_news",
                     "+ Religion*Education2",
                     "+ Religion*Age", 
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m11 <- glmer(m11_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}

m12_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ Technological*Political",
                     "+ Technological*Gender",
                     "+ Technological*type_news",
                     "+ Technological*Education2",
                     "+ Technological*Age",
                     "+ Technological*Religion",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m12 <- glmer(m12_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m13_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ Political*Gender",
                     "+ Political*Education2",
                     "+ Political*type_news",
                     "+ Political*Age",
                     "+ Political*Technological",
                     "+ Political*Religion",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m13 <- glmer(m13_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```


```{r}

m9_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     
                     "+ type_news*Education2",
                     "+ type_news*Age",
                     "+ type_news*Religion",
                     "+ type_news*Technological",
                     "+ type_news*Political",
                     "+ type_news*Gender",

                     
                     "+ Education2*Age",
                     "+ Education2*Religion", 
                     "+ Education2*Technological",
                     "+ Education2*Political",
                     "+ Education2*Gender",
                     
                     "+ Age*Religion",
                     "+ Age*Technological",
                     "+ Age*Political",
                     "+ Age*Gender",
                     
                     "+ Religion*Technological",
                     "+ Religion*Political",
                     "+ Religion*Gender",

                     "+ Technological*Political",
                     "+ Technological*Gender",
                     
                     "+ Political*Gender",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"
                     )

m9 <- glmer(m9_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```







```{r}
summary(m7, corr=FALSE)
```

```{r m1_effects, fig.width = 8, fig.height = 7}
plot(allEffects(m1))
```

```{r m1_odd_ratios, fig.width = 5, fig.height = 5}
plot_model(m1, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```


## Model with interaction terms on the type_news, technology and education
```{r}
m_int_equation = paste0("answer ~ ",
                     "+ Education2",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news",
                     "+ Political",
                     "+ Gender",
                     
                     "+ Education2*type_news",
                     "+ Education2*Political",
                     "+ Education2*Gender",
                     
                     "+ Age*Religion",
                     "+ Age*Technological",
                     "+ Age*type_news",
                     "+ Age*Political",
                     "+ Age*Gender",
                     "+ Education2*Age",

                     
                     "+ Religion*Technological",
                     "+ Religion*type_news",
                     "+ Religion*Political",
                     "+ Religion*Gender",
                     "+ Education2*Religion", 


                     "+ Technological*type_news",
                     "+ Technological*Political",
                     "+ Technological*Gender",
                     "+ Education2*Technological",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")



# Model with all interactions
m_int <- glmer(m_int_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))

```

```{r}
summary(m_int, corr=FALSE)
```

```{r m2_effects, fig.width = 18, fig.height =15}
plot(allEffects(m2), multiline=TRUE,confint=TRUE,ci.style="bars")
```

```{r m2_odd_ratios, fig.width = 15, fig.height = 20}

plot_model(m2, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```

```{r}
tab_model(m2)
```


## Model all interactions


```{r}

m_int_equation = paste0("answer ~ ",
                     "+ Education2",
                     "* Age",
                     "* Religion",
                     "* Technological",
                     "* type_news",
                     "* Political",
                     "* Gender",
                     
   
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")



# Model with all interactions
m_int <- glmer(m_int_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))




```

## Model with selected interactions and main effects
```{r}
m3_equation = paste0("answer ~ ",
                     "+ Education2",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news",
                     "+ Political",

                     "+ Age*Education2",
                     "+ Education2*type_news",
                     #"+ Education2*Political",

                     
                     "+ Age*type_news",
                     "+ Age*Political",
                     
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")




m3 <- glmer(m3_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
capture.output(summary(m3, corr=FALSE),file="./tables/parc_sum.txt")
summary(m3, corr=FALSE)

```

```{r m3_effects, fig.width = 15, fig.height = 8}
plot(allEffects(m3), multiline=TRUE,confint=TRUE)#,ci.style="bars")
```

```{r m3_odd_ratios, fig.width = 8, fig.height = 7}
plot_model(m3, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```


```{r}
tab_model(m3)
```


## Selection of the model

```{r}
anov <- anova(m2,m3, m1)
capture.output(summary(anov),file="./tables/anova_model_selection.txt")
anov
```

## Doing simple Logistic regression without any random effects
```{r}
log_equation  = paste0("answer ~ ",
                       "Political",
                                    "+ Education",
                                    "+ Gender",
                                    "+ Age",
                                    "+ Religion",
                                    "+ Technological",
                                    "+ type_news",
                                    "+ Education*type_news",
                                    "+ Gender*type_news",
                                    "+ Age*type_news",
                                    "+ Religion*type_news",
                                    "+ Technological*type_news",
                                    "+ Political*type_news"
                       )
            
log1= glm(log_equation,
          data=df_education, 
          family="binomial")

```

```{r}
summary(log1, corr=FALSE)
```

```{r log1_effects}
plot(allEffects(log1))
```

```{r log1_odd_ratios}

plot_model(log1, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```

```{r}
tab_model(log1)
```

# Likelihood Ratio Test

```{r}

mixed_lrt_equation = paste0("answer ~ ",
                     " type_news",
                     "+ Gender",
                     "+ Age",
                     "+ Education2",
                     "+ Technological",
                     "+ Political",
                     "+ Religion",
                     "+ type_news*Political",
                     "+ type_news*Education2",
                     "+ type_news*Gender",
                     "+ type_news*Age",
                     "+ type_news*Religion",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)"

                     )

mixed_lrt <- mixed(mixed_lrt_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)), method='LRT')
```

```{r}
nice(mixed_lrt)
```
## Selected model

```{r}
m_final_equation = paste0("answer ~ ",
                     "+ type_news",
                     "+ Age",
                     "+ Religion",
                     "+ Technological",
                     "+ type_news:Age",
                     "+ (1 | news_title)",
                     "+ (1 | id_sondea)")




m_final <- glmer(m_final_equation,
            data=df_education, 
            family="binomial", 
            control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
```

```{r}
summary(m_final, corr=FALSE)
```

```{r log1_effects}
plot(allEffects(m_final))
```

```{r log1_odd_ratios}

plot_model(m_final, vline.color = "red", sort.est = TRUE , show.values = TRUE, value.offset = .3)
```

```{r}
tab_model(m_final)
```















