---
title: "R Notebook"
output: html_notebook
---

```{r}

library(tidyverse, quiet=TRUE) # data wrangling and visualization
library(lme4, quiet=TRUE)     # "golden standard" for mixed-effects modelling in R (no p-values)
library(lmerTest, quiet=TRUE)  # p-values for MEMs based on the Satterthwaite approximation
library(psycho, quiet=TRUE)   # mainly for an "analyze()" function
library(broom, quiet=TRUE)     # for tidy results
library(knitr, quiet=TRUE)     # beautifying tables
library(sjPlot, quiet=TRUE)    # for visualising MEMs
library(effects, quiet=TRUE)   # for visualising MEMs
library(report, quiet=TRUE)    # for describing models
library(emmeans, quiet=TRUE)   # for post-hoc analysis
library(equatiomatic, quiet=TRUE) # for extracting the equation
library(gridExtra) # for grid.arrange() to print plots side-by-side
library(ufs, quiet=TRUE) # For multiple choices questions analysis
library(afex, quiet=TRUE) # For automatic likelihood Ratio Test
```

```{r}
# Knowing package and R version
packageVersion('lme4')
citation('lme4')
```

```{r}
# Set up the script folder as working directory
library(rstudioapi)

# Getting the path of your current open file
current_path = rstudioapi::getActiveDocumentContext()$path 
setwd(dirname(current_path ))
print( getwd() )
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="./plots/")
```

# Load the full dataset
```{r}
df_all = read_csv('../data/cleaned_dataset_per_news.csv')
```

# Function to test overdispersion (not needed for logistic function)
source: http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#overdispersion

```{r}

overdisp_fun <- function(model) {
  rdf <- df.residual(model)
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }

```


### Subsetting the df

```{r}

fixed_effects <- c('Political', 'type_news', 'Education2', 'Education',
                   'Technological', 'Religion', 'Gender', 'Age')
random_effects <- c('id_sondea', 'news_title')
dep_var <- c('answer')
all_var <- c(fixed_effects, random_effects, dep_var)

df_education <- df_all[,all_var] 

df_education[sapply(df_education, is.character)] <- lapply(df_education[sapply(df_education, is.character)], 
                                                           as.factor)

# If want to predict the Right, need to ref "Wrong". No idea why, it is just how it works!
df_education$answer = relevel(df_education$answer, ref="Wrong")
df_education$type_news = relevel(df_education$type_news, ref="true_news")


df_education$Education= relevel(df_education$Education, ref="No university studies")
df_education$Education2= factor(df_education$Education2, levels= c("Secondary", 'College', "University"))

df_education$Technological = factor(df_education$Technological
                                    , levels= c("Basic", "Intermediate", "Advanced"))

df_education$Political = relevel(df_education$Political, ref="Right")
df_education$Religion = relevel(df_education$Religion, ref="Religious")
df_education$Age = factor(df_education$Age, levels=c("<=18-34", "35-54", ">55" ))
df_education$Gender = relevel(df_education$Gender, ref='Male')


df_education <- df_education %>% drop_na()

df_education$answer.num = as.numeric(df_education$answer)-1
```


```{r}
var_just_fake <- c("Previously_read_debunked",
                 "Source_unknown",
                 "Media_unreliable",
                 "Cited_sources_unknown",
                 "Cited_sources_unreliable",
                 "Without_sources",
                 "Unprofessional_style",
                 "No_coherent",
                 "Headline_sensationalist",
                 "Image_sensationalist",
                 "Different_belief",
                 "Different_ideology",
                 "Other")

var_just_true <- c("Previously_read_the_information",
                 "Known_media",
                 "Reliable_media",
                 "Source_known",
                 "Source_Reliable",
                 "Professional_style",
                 "Coherent",
                 "Same_belief",
                 "Same_ideology",
                 "Other")


```

# Analysis for justifications

## Justification thinking it is a Legitimate news

### Multi frequency table for: Justification, people getting wrong on Misinformation

```{r}  
df_fake_wrong <- df_all[str_detect(df_all$type_news, 'fake_news') | str_detect(df_all$answer, 'Wrong')  , ]

all_var <- c(var_just_true)

df_fake_wrong <- df_fake_wrong[,all_var] 

multiFreq_fake_wrong <- multiResponse(df_fake_wrong, var_just_true)
write.csv(multiFreq_fake_wrong, "./tables/justification_fake_wrong.csv", row.names = FALSE)

multiFreq_fake_wrong
```


### Multifrequency table for Justifications, people getting Right on Legitimate information

```{r}  
df_true_right <- df_all[str_detect(df_all$type_news, 'true_news') | str_detect(df_all$answer, 'Right')  , ]

all_var <- c(var_just_true)

df_true_right <- df_true_right[,all_var] 

multiFreq_true_right <- as.data.frame(multiResponse(df_true_right, var_just_true))
write.csv(multiFreq_true_right, "./tables/justification_true_right.csv", row.names = FALSE)

multiFreq_true_right

```

### Z-Test for frequency per proposition accross group


```{r}
# Get the Option into rowname for retrieving the value easily
rownames(multiFreq_true_right) <- multiFreq_true_right$Option
rownames(multiFreq_fake_wrong) <- multiFreq_fake_wrong$Option

# Getting the sample size for both populations
pop_fake_wrong_size = 302
pop_true_right_size = 570



df_all_z_test = NULL

for (Justification in var_just_true)
  {
  
  print(Justification)

  Frequency_False_Wrong = multiFreq_fake_wrong[Justification, 'Frequency']
  Frequency_Legitimate_Right = multiFreq_true_right[Justification, 'Frequency']


  z_test_results <- prop.test(x = c(Frequency_False_Wrong, Frequency_Legitimate_Right),n= c(pop_fake_wrong_size, pop_true_right_size))
  

  

  # For populating df

  
  z_test = z_test_results$statistic
  p_value = z_test_results$p.value
  df_all_z_test = rbind(df_all_z_test, data.frame(Justification, Frequency_False_Wrong, Frequency_Legitimate_Right, z_test,p_value ))


rownames(df_all_z_test) <- NULL

}


df_all_z_test
```

## Justificaiton for when people think it is a False information

### Multi frequency table for:  Justification, people getting Right on Misinformation information

```{r}
df_fake_right <- df_all[str_detect(df_all$type_news, 'fake_news') | str_detect(df_all$answer, 'Right')  , ]

all_var <- c(var_just_fake)

df_fake_right <- df_fake_right[,all_var] 

multiFreq_fake_right <- as.data.frame(multiResponse(df_fake_right, var_just_fake))
write.csv(multiFreq_fake_right, "./tables/justification_fake_right.csv", row.names = FALSE)

multiFreq_fake_right

```


### Multi frequency table for: Justification, people getting Wrong on Legitimate information

```{r}
df_true_wrong <- df_all[str_detect(df_all$type_news, 'true_news') | str_detect(df_all$answer, 'Wrong')  , ]

all_var <- c(var_just_fake)

df_true_wrong <- df_true_wrong[,all_var] 

multiFreq_true_wrong <- as.data.frame(multiResponse(df_true_wrong, var_just_fake))
write.csv(multiFreq_true_wrong, "./tables/justification_true_wrong.csv", row.names = FALSE)

multiFreq_true_wrong

```

### Z-Test for frequency per proposition accross group


```{r}
# Get the Option into rowname for retrieving the value easily
rownames(multiFreq_fake_right) <- multiFreq_fake_right$Option
rownames(multiFreq_true_wrong) <- multiFreq_true_wrong$Option

# Getting the sample size for both populations
pop_true_wrong_size = 198
pop_fake_right_size = 198


df_all_z_test = NULL
for (val in var_just_fake)
  {
  print(val)

  val_true_wrong = multiFreq_true_wrong[val, 'Frequency']
  val_fake_right = multiFreq_fake_right[val, 'Frequency']

  z_test_results <- prop.test(x = c(val_true_wrong, val_fake_right), n = c(pop_true_wrong_size, pop_fake_right_size))
  # For populating df
  Justification = val
  Frequency_Wrong = val_true_wrong
  Frequency_Right = val_fake_right
  z_test = z_test_results$statistic
  p_value = z_test_results$p.value
  df_all_z_test = rbind(df_all_z_test, data.frame(Justification, Frequency_Wrong, Frequncy_Right, z_test,p_value ))
}
#rownames(df_all_z_test) <- df_all_z_test$Justification
rownames(df_all_z_test) <- NULL
df_all_z_test
```
